---
title: "Hello R"
author: "Indira Martinez"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 6
    fig_height: 6
    highlight: haddock
    toc_depth: 10
    theme: spacelab
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

Based on the help file, datasaurus_dozen has 1846 rows and 3 columns. The variables inculded in the data frame are dataset, x-values, and y-values.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=4}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next calculate the correlation between `x` and `y` in the dino dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Now let's plot the data in the star dataset:

```{r plot-star, fig.height=3, fig.width=4}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next calculate the correlation between `x` and `y` in the star dataset:

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise

Now let's plot the data in the circle dataset:

```{r, fig.height=4, fig.width=4}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next calculate the correlation between `x` and `y` in the circle dataset:

```{r}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Here is a plot of all datasets at once.

```{r, fig.height=7, fig.width=6}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+ geom_point()+
  facet_wrap(~ dataset, ncol = 3) + theme(legen.position = "none")
```

Lastly, let's generate all the summary correlation coefficients.

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
```
